% Document body
\section{Web Server Options}
	\subsection{Overview and Criteria}
	For our user interface we will be developing a web application to interface
	with the control system. There three criteria that are needed for our web
	server for this project. The first is that the server will need to run on
	our controller that we chose. The second being that the server will need to
	be reliable on starting up and maintaining the server over long stretches of
	time. The third being memory and processor efficient. The controllers that
	we will be using will have limited memory and we will have other tasks
	running on the same controller so having a server that uses less memory and
	still maintains the features that we require is important.
	\subsection{Potential Choices }
	There is three different web servers that are under consideration. The first
	being Apache. Apache is a HTTP server project produced by Apache Software. The
	second web server is Lighttpd. Lighttpd is a web server that is an open source
	project. The third option is Niginx web service produced by NGINX Software.
	Below we will discuss each of these options and if they meet the criteria
	that is required for this project.
	\subsection{Apache Web Server}
	Apache web server that is developed by Apache Software. It is a widely used
	web server. Reviewing their about page \cite{Apache}, they talk about
	building a stable and advanced web server that is robust, featureful, and
	free for anyone to use. This benefits us since we will not have to pay to use
	this server. Apache web server is also a process based server, this means
	that each connection gets its own thread on the CPU. This allows for if there
	is an error on one connection it does not bring down the whole server. This
	makes the server more reliable and stable. Apache is also for flexible configuration
	.htaccess files. It also comes standard on most Linux servers. Since it is
	one of the more popular options for web server it also has a lot of documentation.
	\\\\
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Stable}: Apache is a very stable web server which his helped
		with how it handles requests in multiple threads.

		\item \textbf{Documentation}: With Apache being one of the most widely used
		web servers there is a lot of documentation. When problems occur this will
		be beneficial.
	\end{itemize}

	\noindent\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{Resources}: The drawback of having head request
		handled by a single thread on the CPU is that it requires more resources
		compared to the alternatives.
	\end{itemize}

	\subsection{Lighttpd Web Server}
	Lighttpd web server is a lightweight web server that is designed to be secure,
	fast, flexible and is optimized for high-performance. From their website \cite{Lighttpd}
	they state that they use non-blocking I/O event loop for running each single
	process that comes to the server. They talk about how the have a low memory
	footprint. Lighttpd is also an asynchronous server compared to Apache which is
	a synchronous server. Below are the advantages and disadvantages of using
	Lighttpd Web Server for our project.
	\\\\
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Fast and Lightweight}: With the server running on one thread
		and assigning working threads as well as the system uses non-blocking I/O
		event looping the server uses very little resources.
	\end{itemize}
	\noindent\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{Not as Stable}: With the server running a single master thread
		and assigning worker threads, if something goes wrong with a connection casuing
		that thread to crash you lose the whole server.
		\item \textbf{Documentation}: With Lighttpd not as widely used, there
		is less documentation surrounding it. This can make solving problems down the
		road more difficult.
	\end{itemize}
	\subsection{Nginx Web server}
	Nginx is an open source web server developed by Nginx software. It is another
	asynchronous lightweight HTTP server. It differs from apache by that it has
	one master process to server requests. It then delegates tasks to worker
	proccess. This allows it to be very fast and efficient when serving static
	web pages. \cite{Nginx}. Below are the advantages and disadvantages
	of using Nginx web server for our project.
	\\\\
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Fast and Lightweight}:With the server running on one thread
		and assigning working threads as well as the system uses non-blocking I/O
		event looping the server uses very little resources.
		\item \textbf{Documentation}: Nginx is more widely so there is more documentation.
		This will allow us to more quickly solve problems when they occur.
	\end{itemize}
	\noindent\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{Not As Stable}: With the server running a single master thread
		and assigning worker threads, if something goes wrong with a connection casuing
		that thread to crash you lose the whole server.
	\end{itemize}
	\subsection{Discussion}
	Apache, Lighttpd, Nginx, they all handle serving web pages and processing
	request slightly differently. Apache for example uses a processes based approach.
	Meaning that each request gets its own thread on the CPU, this does require
	some overhead when it comes to resource. This is in contrast to both Lighttpd
	and Nginx web servers which are asynchronous servers are mainly event-driven
	and run on a single process and split into worker tasks from there to complete
	tasks. This makes them a little faster and requires less total resources to run.
	There is a problem with running a single master process if there is a problem
	with the connection it could bring the whole server down which would not happen to an Apache server since each
	connection is in its own thread. All three technologies meet the criteria for r
	reliability, efficiency, and controller compatibility, but each has its own
	advantage
	\subsection{Conclusion}
	Looking at all three options, chosen to go with the Apache web server.
	This web service will only server web pages to a limited number of clients.
	One of the main criteria that we were worried about was that
	it would be stable once we had it working. Apache being one of the most stable
	web servers due to it using a process based server if a problem occurs with
	the connections then it won’t bring down the whole system. With that it meets
	all of our criteria for our project.
\newpage
\section{Mobile Options}
	\subsection{Overview and Criteria}
	As mobile computing becomes more and more popular it is important to take
	that into consideration when designing products today. With mobile becoming
	more important in today's world we would like to add a mobile option to interface
	with our system. When choosing which option we would like to go with when
	incorporating mobile we have to look at three key criteria. The first being
	that it works on multiple mobile platforms, Android, and IOS. The second being
	that we would like it to be consistent with how the user interacts with the
	product.
	\subsection{Potential Choices}
	When looking at mobile options there are three main options to look at. The
	first being building a native mobile application for each platform. The second
	being building a mobile friendly web interface.The final one being building
	a dedicated mobile site which will be served to the user if requested from
	a mobile device.
	\subsection{Native Mobile Application}
	Building a native app for mobile  Building a native mobile
	app has several advantages and disadvantages when it comes to working with
	products.
	\\\\
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Full Mobile Friendly}: This is designed and implemented with
		mobile in mind. Making it a more friendly mobile environment.
		\item \textbf{Quick Load Times}: With the app fully contained on the mobile
		it does not have pull a web page from a server.
	\end{itemize}
	\noindent\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{Developing and Maintaining Multiple Platforms}: With designing
		and creating a native mobile app you have to create it on two different platforms.
		This can be time consuming.
	\end{itemize}
	\subsection{Build Mobile Friendly Website}
	Wth building a mobile friendly website we would develop the site with mobile
	in mind. Building a mobile friendly website has several advantages and disadvantages
	when working with products. Below are listed the advantages and disadvantages
	for building a mobile friendly website.
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Consistent With Desktop Content}: This would allow the desktop
		and mobile environments to feel consistent and not make users learn two
		different interfaces
		\item \textbf{Less To Maintain}: Only once site needs to be built making
		maintaining the site easier.
	\end{itemize}
	\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{General Usability}: Changing settings or checking the same
		information might be more difficult on a mobile platform due to how they go
		through the pages.
		\item \textbf{Slower Loading Times}: With the amount of information pushed
			back and forth between the device and could be slower due to it going over
			3g or 4g speeds.
	\end{itemize}
	\subsection{Build Mobile Dedicated Site}
	Building a dedicated mobile app would be creating the site again but more
	mobile friendly and delivering that to mobile devices instead of the desktop
	site. Below are the advantages and disadvantages of creating a mobile dedicated site.
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Mobile Focused}: With building a mobile dedicated site it allows
		you to make it more mobile friendly.
		\item \textbf{Consistent Style}: It allows for you to tweak the style of the
		main site to allow for it to be more mobile friendly but still keep its look
		and feel.
	\end{itemize}
	\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{Increased Maintains Time/Cost}: With having two sites to maintain,
		you will have to put more time and energy creating and maintaining it.
		\item \textbf{Slower Service}: Since the server has to check what type of
		device that is requesting the page it takes some processing time.
	\end{itemize}
	\subsection{Discussion}
	Looking at all three options they all have advantages and disadvantages. For
	our project we are looking at a few key criteria and those are that it has to
	work on multiple platforms and that it needs to be consistent with the desktop
	environment. All three can easily be made to be consistent with the desktop
	environment. With building native application for mobile that would require
	applications developed for both Android and IOS. This is time consuming and
	difficult to maintain as a change in one would require a change in the other.
	This is in contrast to the other two options, where both of them will work on any device
	given that it has a browser. Looking at the other two options they both have very
	similar advantages and disadvantages. The main disadvantage to building a dedicated
	mobile site is that you will have to build and maintain two sites which compared to
	building a mobile friendly website where you just have to maintain one site.
	They both meet both criteria we have for our mobile options and are both strong
	options.
	\subsection{Conclusion}
	Between the three options, building a native mobile application, building a
	mobile dedicated site and building a mobile friendly site we choose to go with
	building a mobile friendly site. With keeping mobile devices in mind from the
	beginning of the web interface it makes it easier to develop and maintain over
	time. This also cuts down on development time over all as we only need to
	create one web site.
\section{Moisture Sensors}
	\subsection{Overview and Criteria}
	We would like to be able to add moisture sensors
	to the enclosure to monitor the moisture of the soil the plants are in to
	get an idea of when you should water your plants. To do this we have several
	criteria that we have to look at. The first being that it must be able to
	interact with our chosen microcontroller. The second being that it must
	read the moisture of the soil.
	\subsection{Potential Choices }
	There are three different choices that we could go with. The first is going
	with an Octopus soil moisture sensor from Elecfreaks \cite[pg 2] {Octopus_soil_sensor},
	We could design and custom print our own moisture sensors or we could go with
	a SparkFun Soil Moisture Sensor from SparkFun \cite[pg 2] {SparkFun_Soil_Moisture_Sensor}.
	\subsection{Octopus Soil Moisture Sensor}
	Octopus soil moisture sensor is a moisture sensor that can be purchased through
	Elecfreaks. This sensor is a lot like other moisture sensors in shape and how
	it connects to a micro controller. The way this moisture sensor is unique is
	that it can connect to the sensor modules. This can connect to any arduino
	based microcontroller.
	\\\\
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Time Investment}: With the sensors already built the only time
		need is to configure and install the sensors.
		\item \textbf{Cost}: For the first initial prototypes it is cheaper to use
		these.
	\end{itemize}
	\noindent\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{Not Customizable}: We are not able to design the shape or features
		it monitors.
	\end{itemize}
	\subsection{Design and Print Own Sensors}
	One option would be to design our own sensor using a program like Eagle and
	have it printed and sent to use. The advantage to this is that we can make the
	sensor exactly how want it in the shape that would fit in our enclosure. This
	would also be ideal if we need a bunch of them. The disadvantage for this would
	that we would have to spend time designing it and then have to wait for them
	to print. This would only be ideal if we were going through to a production
	unit.
	\\\\
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Customizable}: With designing and building our own sensors
		we can add only the features that are needed for the project.
		\item \textbf{Cost}: This is the cheapest options when buying large quantities.
	\end{itemize}
	\noindent\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{Large Investment}: To design and have the sensors made would
		take a large investment of time and money. In the long run it would be advantageous
		to do this if this goes to production.
	\end{itemize}
	\subsection{SparkFun Soil Moisture Sensor}
	SparkFun soil moisture sensor  be purchased through Sparkfun. It can be used
	with any arduino microcontroller. This allows us to be able monitor the soil
	moisture. The SparkFun soil moisture sensor is a lot like many other sensors
	in design and how it interfaces with microcontrollers.
	\\\\
	\textbf{Advantages}:
	\begin{itemize}
		\item \textbf{Time Investment}: With the sensors already built the onlly time
		need is to configure and install the sensors.
	\end{itemize}
	\noindent\textbf{Disadvantages}:
	\begin{itemize}
		\item \textbf{Not Customizable}: We are not able to design the shape or features
		it monitors.
		\item \textbf{Cost}: These are more expensive than other sensors on the market.
	\end{itemize}
	\subsection{Discussion}
	Moisture sensors are simple sensors so most of them are similar in shape,
	size and how they read in moisture. For this reason it is possible to design
	our own and get it the shape and size that we would like. The disadvantage of this
	is that we would have to design it and then have them printed and they are
	not guaranteed to work. This is why the other two options were chosen. The
	Octopus Soil Moisture Sensor and the Sparkfun Soil Moisture Sensor are very similar
	The Octopus soil moisture sensor has the ability to connect to other sensors.
	This is a nice feature if we would like to add any other sensors. The SparkFun
	Soil moisture sensor doesn't have any special feature other than reading in
	the moisture level. Though it is more expensive than the Octopus moisture sensor.
	\subsection{Conclusion}
	Looking at all the options it seems like the Octopus soil moisture sensor is
	the option we will be going with. Designing and having it printed would be
	time consuming and expensive up front. The SparkFun soil moisture sensor is
	has all the features that we need but is more expensive than the Octopus soil.
	The added cost of this sensor makes Octopus soil moisture sensor the sensor
	we will be using for our project.

